---
title: "Arrival Rates"
author: "Emmett & Rachel"
format: pdf
editor: visual
---


Arrival Rates
```{r}
#load libraries 
library(tidyverse)
```


```{r}
#'Average Arrival Rates for Bike Share Program
#' @description finds the average arrival rates of bikes in the data per 
#' @param cleaned_bike_df cleaned data frame of starting stations, destination stations, and time of the bikes leaving  (DOUBLE CHECK)
#' @return x_hat the (FINISH)

arrival_rates <- function(cleaned_bike_df){

#First, we don't need the observations where bikes are reset by the company—this is irrelevant to how many people are using bikes on a given day.

#make sure start_time and end_time are correct formats mutate(start_time = as.POSIXct(start_time, format = "%Y-%m-%d %H:%M:%S"),end_time = as.POSIXct(end_time, format = "%Y-%m-%d %H:%M:%S"))%\>%

#create hour and day variables for use in functions #though our original data set has the same details for start and end times, we assume this will likely not be the case for all data.

return(x_hat_df) 
}
